---
title: "Stockr - Interactive Stock Viewer"
subtitle: "Track your portfolio in real-time"
format: html
engine: knitr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(plotly)
library(dplyr)
library(duckdb)
library(crosstalk)
library(htmltools)
```

## Welcome to Stockr

Interactive stock price tracking with real-time charts and filtering.

```{r load-data}
# Load stock data
con <- dbConnect(duckdb(), dbdir = "data/stocks.duckdb", read_only = TRUE)
stock_data <- dbGetQuery(con, "SELECT * FROM stock_prices ORDER BY date DESC")
dbDisconnect(con)

# Convert date to proper format and sort
stock_data$date <- as.Date(stock_data$date)
stock_data <- stock_data %>% arrange(ticker, date)

# Get unique tickers and date range
tickers <- unique(stock_data$ticker)
date_min <- min(stock_data$date)
date_max <- max(stock_data$date)

# Shared data for client-side filtering
sd <- SharedData$new(stock_data, key = ~ticker, group = "ticker")
```

## 🎛️ Ticker Selection

Use the dropdown to pick one of the preselected tickers (SLV, NVDA, AAPL, ADBE, MP). You can also type another ticker symbol; if it's present in the dataset it will display. To add a brand-new ticker, run the fetch script with that symbol and re-render.

```{r ticker-filter}
filter_select(
  id = "ticker",
  label = "Select ticker (type to search or add):",
  sharedData = sd,
  ~ticker,
  multiple = FALSE
)
```

## 📊 Stock Price Chart

```{r price-chart}
# Create interactive price chart
p1 <- plot_ly(sd, x = ~date, y = ~close, type = 'scatter', mode = 'lines',
          name = ~ticker, color = ~ticker) %>%
  layout(
    title = "Stock Price History",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Price ($)"),
    hovermode = "x unified",
    template = "plotly_white",
    height = 500
  )

p1
```

## 🕯️ Candlestick Chart

```{r candlestick-chart}
# Create candlestick chart
p_candle <- sd %>%
  plot_ly(x = ~date, type = "candlestick",
          open = ~open, close = ~close,
          high = ~high, low = ~low,
          name = ~ticker) %>%
  layout(
    title = "OHLC Candlestick Chart",
    xaxis = list(
      title = "Date",
      rangeslider = list(visible = FALSE)
    ),
    yaxis = list(title = "Price ($)"),
    template = "plotly_white",
    height = 500
  )

p_candle
```

## 📈 Trading Volume

```{r volume-chart}
# Create volume chart
p2 <- plot_ly(sd, x = ~date, y = ~volume, type = 'bar',
          name = ~ticker, color = ~ticker) %>%
  layout(
    title = "Trading Volume",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Volume"),
    hovermode = "x unified",
    template = "plotly_white",
    height = 400
  )

p2
```

## 📋 Data Summary

```{r data-table}
library(knitr)

# Show summary statistics
summary_stats <- stock_data %>%
  group_by(ticker) %>%
  summarise(
    Records = n(),
    First_Date = format(min(date), "%Y-%m-%d"),
    Last_Date = format(max(date), "%Y-%m-%d"),
    Min_Price = paste0("$", round(min(close), 2)),
    Max_Price = paste0("$", round(max(close), 2)),
    Avg_Price = paste0("$", round(mean(close), 2)),
    Current_Price = paste0("$", round(last(close), 2)),
    .groups = 'drop'
  )

kable(summary_stats, format = "html")
```

## 📅 Latest Prices (Last 30 Trading Days)

```{r recent-prices}
recent <- stock_data %>%
  arrange(desc(date)) %>%
  slice_head(n = 30) %>%
  arrange(date) %>%
  select(Date = date, Ticker = ticker, Open = open, High = high, 
         Low = low, Close = close, Volume = volume) %>%
  mutate(
    Open = paste0("$", round(Open, 2)),
    High = paste0("$", round(High, 2)),
    Low = paste0("$", round(Low, 2)),
    Close = paste0("$", round(Close, 2)),
    Volume = format(Volume, big.mark = ",")
  )

kable(recent, format = "html")
```

## 📊 Price Range Distribution

```{r price-distribution}
# Create histogram of closing prices
p3 <- plot_ly(sd, x = ~close, type = 'histogram', nbinsx = 50,
          name = 'Price Distribution',
          marker = list(color = 'rgba(52, 152, 219, 0.7)')) %>%
  layout(
    title = "Closing Price Distribution",
    xaxis = list(title = "Price ($)"),
    yaxis = list(title = "Frequency"),
    template = "plotly_white",
    height = 400
  )

p3
```

---

**Data Source:** Yahoo Finance  
**Last Updated:** `r format(max(stock_data$date), '%Y-%m-%d')`  
**Records:** `r nrow(stock_data)` pricing records
